---
title: "Logistics Regression - Titanic Dataset"
author: "Olanrewaju Titilola"
date: "2024-02-18"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load Library packages
```{r}
library(tidyverse)
library(knitr)
library(ggplot2)
library(dplyr)
library(forcats)
library(caret)
```

# Set work directory
```{r}
setwd("~/UPLIFT/Course 2/Course 2 - Assignments/Assignment 4 - Logistics Regression")

```

## TRAIN DATASET

#Load datasets
```{r}
train_data<-read.csv("train.csv", header = TRUE)
head(train_data, 5)
```
# Calculate and replace missing values in Age column with the mean of all ages

```{r}
train_data$Age[is.na(train_data$Age)]=mean(train_data$Age, na.rm = TRUE)
```

```{r}
view(train_data)
```

# Load Test Dataset
```{r}
test_data<-read.csv("test.csv", header=TRUE)
head(test_data, 5)
```
# Calculate and replace missing values in Age column with the mean of all ages

```{r}
test_data$Age[is.na(test_data$Age)]= mean(test_data$Age,na.rm = TRUE)
```

# Check the types of dataset
```{r}
str(test_data)
```


# Create dataframe of dependent/independent variables
```{r}
nonvars<-c("PassengerId","Name","Ticket","Cabin","Embarked")
train_data<-train_data[,!(names(train_data)%in%nonvars)]
str(train_data)
```


## Develop a model for training dataset
```{r}
train_model<-glm(Survived~.,data= train_data,family=binomial)
summary(train_model)
```

# Prediction of survival on Test dataset
```{r}
test_data$predict <- predict(train_model, type = "response", newdata = test_data)
summary(test_data$predict)

```

# No preference over error t = 0.5
```{r}
test_data$survived <- as.numeric(test_data$predict>=0.5) 
table(test_data$survived)

```

```{r}
predictions= data.frame(test_data[c("PassengerId","survived")])
write.csv(file = "TitanicPred", x=predictions,)
head(predictions,5)
```


## Interpretation of the Coefficients:


### Pclass (Passenger Class) (-1.082896):
**For each decrease in the passenger class, the estimated probability of survival decrease by about 1.08. Lower class is associated with lower chances of survival.**

### Sexmale (-2.763615):
**Being a male reduces the estimated probability of survival by about 2.76.Being a male significantly decreases the chances of survival compared to females.**

### Age (-0.039746):
**For each year increase in age, the estimated probability of survival decrease by about 0.04.Getting older is associated with a slight decrease in the chances of survival.**

### SibSp (Siblings/Spouses) (-0.351246):
**For each additional sibling or spouse onboard, the estimated probability of survival decrease by about 0.35. Having more siblings or spouses onboard is associated with lower chances of survival.**


